---
title: "R Crawler 101"
subtitle: ""
author: 
    name: "Kyle Chung"
    affiliation: "Trend Micro, Data Scientist"
    email: "kylechun9@gmail.com"
    website: "https://github.com/everdark"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
    html_document:
      theme: united
      toc: yes
abstract: This is the abstract.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE)
options(width=120)
library(data.table)
library(stringr)
library(httr)
```

----------------------
## Facebook Graph API | Introduction
### the UI for exploration
+ [Facebook Graph API Explorer](https://developers.facebook.com/tools/explorer)
+ need a valid *access token*
+ the token will expire in hour (can be refresh)

### components of the API
+ nodes
    + *objects*: a User, a Photo, a Page, a Comment, ...
+ edegs
    + *connections* between objects
+ fields
    + *information* about objects

### baisc syntax
`/<node_id>/<edge_name>?fields=f1,f2,...`

+ try the special `me` node: `me/photos?fields=from`

## Facebook Graph API | Crawling
## Regular Expression
## Regular Expression in R


### Appendix

```{r sessionInfo}
sessionInfo()
```


### References


